Appendix 2 - Fitting proposed path models using the C-statistic

### 2015-03-17 report_dbh_problems.Rmd
Added review of `alive` stems that showed negative growth

This is summarizing changes I made to the Sonoma Access Database DBH measurements based on data exploration in the `explore_data.R` document. There were 100 stems that had a negative change in DBH of greater than 5 cm, and 62 of these were alive in the 2014 remeasurement. This reports on the stems still alive in 2014 that I could logically make corrections to, and so avoid the incredible dramatically shrinking tree. Stems that are not explicitly listed

#### Stems with a negative change in DBH > 15 cm (14)
 - For stems 4797 & 4795 I calculated an estimate for the original DBH based on a linear relationship between measurements from 2012 and 2014 because the original measurements recorded were most likelyl circumference. I initially did a simple coversion from circumference to diameter, but this resulted in values that were substantially hire than the measurements in either 2012 or 2014. New values for 2009 will be: stem 4797: 7.8, stem 4795: 10.0

 - Replaced 2004 value (31.5) for stem 945 by treating that as teh circumference, so new initial diameter is 10

@@

 I changed values for 6 of 18 stems

>>>>

This is summarizing changes I made to the Sonoma Access Database DBH measurements based on data exploration in the `explore_data.R` document. There were 100 stems that had a negative change in DBH of greater than 5 cm, and 62 of these were alive in the 2014 remeasurement. This reports on the stems still alive in 2014 that I could logically make corrections to, and so avoid the incredible dramatically shrinking tree.

#### Stems with a negative change in DBH > 15 cm (14)
 - For stems 4797 & 4795 I calculated an estimate for the original DBH based on a linear relationship between measurements from 2012 and 2014 because the original measurements recorded were most likelyl circumference. I initially did a simple coversion from circumference to diameter, but this resulted in values that were substantially hire than the measurements in either 2012 or 2014. New values for 2009 will be: stem 4797 = 7.8, stem 4795 = 10.0

 - Replaced 2004 value (31.5) for stem 945 by treating that as the circumference, so new initial diameter is 10

@@

I changed values for 6 of 18 stems.

In total, there are now 30 stems with 'Alive' status in 2014 that still have negative growth values > 5cm, so I was able to make corrections for just over half of the 62.

So I think this covers all the stems I was considering for errors due to shrinkage. I still need to examine the outliers on the positive growth side.

#### These stems had > 20cm growth
plot    cluster   tag   species year year_dbh1 status delta_dbh dbh1  dbh2
BOUV01       2    1321    QUAG 2014      2005  Alive      22.1 98.7 120.8 *ok*        
***BOUV02       4    1325    QUAG 2014      2005  Alive      23.0 63.4  86.4***
BOWES02      2    423b    UMCA 2014      2004  Alive      31.2 22.0  53.2 *ok*       
COOK02       3    472     UMCA 2014      2005  Alive      30.0 16.1  46.1 *ok*       
***LAZY05       2    2073    QUKE 2014      2004  Alive      34.0 63.8  97.8***      
PFEND02      2    4516    UMCA 2014      2004  Alive      27.1 30.5  57.6 *ok*
SKILE01      4    3288    UMCA 2014      2004  Alive      24.4 18.7  43.1 *ok*       
SKILE01      4    3290    UMCA 2014      2004  Alive      21.7 41.2  62.9 *ok*

The two rows that are ***bold italic*** are stems that I definitely want to double check the entries on the original data sheets.
